Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-22 article.tex
More updates for Sec 4

The current work considers three forms of the problem:
\begin{enumerate}[label=\roman*.]
	\item Small strain linear elastic \cite{Zienkiewicz2000}: $E=70$ MPa, $\nu=1/3$, and $\tau = 6.25$ MPa.
	\item Finite strain neo-Hookean hyperelastic \cite{dealII95}: $E=1.0985$ MPa, $\nu=0.3$, and $\tau = 0.0625$ MPa.
	\item Finite strain elastoplastic \citep{Simo1992}: $E=206.9$ MPa, $\nu=0.29$, $\sigma_y = 0.45 + 0.12924\bar{\varepsilon}_p + (0.715 - 0.45)(1- e^{-16.93\bar{\varepsilon}_p})$ MPa, and $\tau = 0.3125$ MPa.
\end{enumerate}
where $E$ is the Young's modulus, $\nu$ is the Poisson's ratio, $\sigma_y$ is the yield strength, $\bar{\varepsilon}_p$ is the equivalent plastic strain, and $\tau$ is the prescribed shear traction.

@@

The equivalent stress distribution in the cantilever at maximum deflection is shown in Figure \ref{fig:dynamic_cantilever} for the mesh with $2\,160$ cells.
Figure \ref{fig:dynamic_cantilever_results}
\begin{figure}[htbp]
   \centering
	\subfigure[Deflection vs time for the four meshes using a time step of 0.001617274174 s]
	{
   		\includegraphics[width=0.45\textwidth]{figures/cantilever_disp} 
   	}
	\subfigure[XXX]
	{
   		\includegraphics[width=0.45\textwidth]{figures/placeholder}  
   	}
   \caption{Vibration of a 3-D Cantilevered Beam case}
   \label{fig:dynamic_cantilever_results}
\end{figure}

@@

\paragraph{Case 8: Elastic plate behind a rigid cylinder}
\citet{Turek2006} proposed this well-known fluid-solid interaction benchmark case as an extension of the classic flow around a cylinder in a channel problem \cite{Ferziger2002}.
The \texttt{FSI3} variant of the case examined here (Figure \ref{fig:hronTurek-geometry} consists of a horizontal channel (0.41 m in height, 2.5 m in length) with a rigid cylinder of radius 0.05 m, where the cylinder centre is 0.2 m from the bottom and inlet (left) boundaries.
A parabolic velocity is prescribed at the inlet velocity with a mean value of 2 m/s.
A St.\ Venant-Kirchhoff hyperelastic plate ($E = 5.6$ MPa, $\nu = 0.4$) of 0.35 m in length and 0.02 m in height is attached to the right-hand side of the rigid cylinder.
The fluid's kinematic viscosity is 0.001 m$^2$/s and density is 1000 kg/m$^3$, while the solid's density is $10\,000$ kg/m$^3$.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.6\textwidth]{figures/hronTurek-geometry} 
   \caption{Elastic plate behind a rigid cylinder case geometry and mesh (taken from \citet{Tukovic2018a})}
   \label{fig:hronTurek-geometry}
\end{figure}

\hl{Describe mesh}
\hl{Describe time step and tolerances}

\hl{Give results: snapshot of max deformation; force or displacement vs benchmark}

>>>>

The current work considers three forms of the problem:
\begin{enumerate}[label=\roman*.]
	\item Small strain linear elastic \cite{Zienkiewicz2000}: $E=70$ MPa, $\nu=1/3$, and $\tau = 6.25$ MPa \hl{E is too low or tau is too high as disps are very large}.
	\item Finite strain neo-Hookean hyperelastic \cite{dealII95}: $E=1.0985$ MPa, $\nu=0.3$, and $\tau = 0.0625$ MPa.
	\item Finite strain elastoplastic \citep{Simo1992}: $E=206.9$ MPa, $\nu=0.29$, $\sigma_y = 0.45 + 0.12924\bar{\varepsilon}_p + (0.715 - 0.45)(1- e^{-16.93\bar{\varepsilon}_p})$ MPa, and $\tau = 0.3125$ MPa.
\end{enumerate}
where $E$ is the Young's modulus, $\nu$ is the Poisson's ratio, $\sigma_y$ is the yield strength, $\bar{\varepsilon}_p$ is the equivalent plastic strain, and $\tau$ is the prescribed shear traction.

@@

The equivalent stress distribution in the cantilever at maximum deflection is shown in Figure \ref{fig:dynamic_cantilever} for the mesh with $2\,160$ cells.
Figure \ref{fig:dynamic_cantilever_results}
\begin{figure}[htbp]
   \centering
	\subfigure[Deflection vs time for the four meshes using a time step of 0.001617274174 s]
	{
   		\includegraphics[width=0.55\textwidth]{figures/cantilever_disp} 
   	}
	\subfigure[XXX]
	{
   		\includegraphics[width=0.25\textwidth]{figures/placeholder}  
   	}
   \caption{Vibration of a 3-D Cantilevered Beam case}
   \label{fig:dynamic_cantilever_results}
\end{figure}

\hl{maybe we should state the nonlinear/linear solver settings for completeness}

@@

\paragraph{Case 8: Elastic plate behind a rigid cylinder}
\citet{Turek2006} proposed this well-known fluid-solid interaction benchmark case as an extension of the classic flow around a cylinder in a channel problem \cite{Ferziger2002}.
The \texttt{FSI3} variant of the case examined here (Figure \ref{fig:hronTurek-geometry} consists of a horizontal channel (0.41 m in height, 2.5 m in length) with a rigid cylinder of radius 0.05 m, where the cylinder centre is 0.2 m from the bottom and inlet (left) boundaries.
A parabolic velocity is prescribed at the inlet velocity with a mean value of 2 m/s.
A St.\ Venant-Kirchhoff hyperelastic plate ($E = 5.6$ MPa, $\nu = 0.4$) of 0.35 m in length and 0.02 m in height is attached to the right-hand side of the rigid cylinder.
The fluid's kinematic viscosity is 0.001 m$^2$/s and density is 1000 kg/m$^3$, while the solid's density is $10\,000$ kg/m$^3$.
\begin{figure}[htbp]
   \centering
	\subfigure[Geometry (taken from \citet{Tukovic2018a})]
	{
	   \includegraphics[width=0.7\textwidth]{figures/hronTurek-geometry} 
   	}
	\subfigure[Mesh containing $5\,336$ cells in the fluid region and 630 cells in the solid region, where a closeup of the plate is shown in the right]
	{
   		\includegraphics[width=0.4\textwidth]{figures/hronTurek-mesh}  
   		\includegraphics[width=0.4\textwidth]{figures/hronTurek-mesh-zoom}  
   	}
   \caption{Elastic plate behind a rigid cylinder case geometry and mesh }
   \label{fig:hronTurek-geometry}
\end{figure}

A quadrilateral mesh is employed with $5\,336$ cells in the fluid region and 630 cells in the solid region.
The total simulation time is 6 s, and the time-step size is 1 ms. 
The interface- quasi-Newton with inverse Jacobian from a least-squares model coupling approach \cite{Degroote2009} is employed for the fluid-solid interaction coupling.
Further details of the fluid-solid interaction procedure are found in \citet{Tukovic2018a}.
\hl{State tolerances}

Figure \ref{fig:hronTurek-results}(a) shows the velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s, corresponding to the maximum displacement of the plate.
The predicted vertical displacement of the end of the plate vs time is compared with the results from the \citet{Turek2006} benchmark in Figure \ref{fig:hronTurek-results}(b).
\begin{figure}[htbp]
   \centering
	\subfigure[Velocity field in the fluid region and displacement magnitude in the solid region at $t = 4.42$ s]
	{
	   \includegraphics[width=0.8\textwidth]{figures/hronTurek-results} 
   	}
	\subfigure[Vertical displacement of the end of the plate vs time]
	{
   		\includegraphics[width=0.3\textwidth]{figures/placeholder}  
   	}
   \caption{Elastic plate behind a rigid cylinder case results}
   \label{fig:hronTurek-results}
\end{figure}
